Efficient Community Formation \\ for Web Services

### 2013-12-21 papers/coalition-journal-R1/coalition_journal_r1.tex
changes

\textbf{Contributions.} In this paper, we use game theory to
propose a cooperative game model for the aggregation of web
services within communities. The solution concepts of our
cooperative game seeks to find efficient ways of forming
coalitions (teams) of web services so that they can maximize their
gain and payoff, and distribute the gain in a fair way among all
the web services. Achieving fairness when the gain is distributed
among the community members is the main factor to keep the
coalition stable as no web service will expect to gain better by
deviating from the community. In other words, the coalition is
made efficient if all the members are satisfied. We analyze the
game model using two scenarios. The first one simply considers one
community and many web services interested to join it. The second
scenario, which generalizes the first one, includes the
possibility of joining different already established communities.
We first propose a representation function for communities of web
services based on their QoS attributes. By using this function, we
can evaluate the $worth$ of each community of web services. When
facing new membership requests, a typical community master checks
whether the new coalition having the old and new set of web
services will keep the community stable or not. The community
master will reject the membership requests if it finds out that
the new coalition would be unstable, preventing $any$ subset of
web services from gaining significantly more by deviating from the
community and joining other communities or forming new ones. The
computation of solutions for cooperative game theory problems is
combinatorial in nature and proven to be NP-complete
\cite{Algorithmic}, making this computation impractical in real
world applications. However, using the concepts of coalition
stability, we propose approximation algorithms running in
polynomial time providing web services and community masters with
applicable and near-optimal decision making mechanisms.

@@

%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 3 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table*}[!t]
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
\caption{Example 3} \label{example_3} \centering
\begin{tabular}{c c c c}
\hline
$WS$ & $QoS_{ws}$ & $Th_{ws}$ & $\text{\emph{Input Task Rate}}$\\
\hline
1 & 0.8 & 10 & 5\\
2 & 0.8 & 20 & 5\\
3 & 0.8 & 30 & 5\\
\hline\\
\end{tabular}
%\end{table}
%
%\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
% \caption{Three web services}
\label{example_3_2} \centering
\begin{tabular}{l l || l l}
\hline
Community & Worth & Community & Worth\\
\hline
$\left\{C_{ms_1}\right\}$ & 0 & $\left\{C_{ms_2}\right\}$ & 0\\
$\left\{C_{ms_1}, ws_1\right\}$ & 8 & $\left\{C_{ms_2}, ws_1\right\}$ & 8\\
$\left\{C_{ms_1}, ws_2\right\}$ & 16 & $\left\{C_{ms_2}, ws_2\right\}$ & 16\\
$\left\{C_{ms_1}, ws_3\right\}$ & 16 & $\left\{C_{ms_2}, ws_3\right\}$ & 24\\
$\left\{C_{ms_1}, ws_1, ws_2\right\}$ & 16 & $\left\{C_{ms_2}, ws_1, ws_2\right\}$ & 24\\
$\left\{C_{ms_1}, ws_1, ws_3\right\}$ & 16 & $\left\{C_{ms_2}, ws_1, ws_3\right\}$ & 32\\
$\left\{C_{ms_1}, ws_2, ws_3\right\}$ & 16 & $\left\{C_{ms_2}, ws_2, ws_3\right\}$ & 32\\
$\left\{C_{ms_1}, ws_1, ws_2, ws_3\right\}$ & 16 & $\left\{C_{ms_2}, ws_1, ws_2, ws_3\right\}$ & 32\\
$\left\{C_{ms_1}, C_{ms_2}, ...\right\}$ & 0 & $\left\{ws_1\right\}$ & 6.8\\
$\left\{ws_2\right\}$ & 4.2 & $\left\{ws_3\right\}$ & 6.8\\
\hline
Community $R_{C_1}$: 20 \\ Community $R_{C_2}$: 40\\
\hline
\end{tabular}
\end{table*}
%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 3 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In Example 3, we consider the case of having different communities
with different market shares represented by ${R_C}$ values. Web
services also have a small share of market independently,
providing them with a small task pull. In these kind of scenarios,
the solution considers individual maximization of payoff and also
the total worth of all communities which represents the
\emph{social welfare}. In this example, the most efficient
partition of web services is earned by having two coalitions of
$\left\{C_{master_1}, ws_2\right\}$ and $\left\{C_{master_2},
ws_1, ws_3\right\}$, which yields a total value of $32 + 16 = 48$.
In these types of scenarios, the goal is to reach stability,
adopting a distributed approach where all players have the power
to decide about joining a coalition or not. The communities
usually start the game having some established members. They may
exchange web services and new web services would join them having
at least one player gaining utility without hurting any other
participant. In this example, if we initially having two
coalitions of $\left\{C_{master_1}, ws_2\right\}$ and
$\left\{C_{master_2}, ws_1\right\}$ and a ${ws_3}$ as new web
service, ${ws_3}$ joining ${C_{master_1}}$ would hurt at least
itself or $ws_2$; however, ${ws_3}$ joining ${C_{master_2}}$ would
not hurt any participant and ${ws_3}$ would earn more within the
community and the community will have enough web services
performing the incoming tasks from users.

The first two examples illustrate the fact that a community cannot
simply increase its revenue by adding more web services. The web
services and even community owners are autonomous agents and would
deviate and be displeased about the community if new members cause
a drop in their profit. The job of the community master is to
attract as many quality web services it can and keep them
satisfied; hence the group stability is guaranteed. The third
example highlights another type of problem we would like to
address, which is how to form best possible groups of communities,
and allocate web services among communities in a way which would
maximize the payoff of members already residing in the
communities. In the next section, we provide algorithms based on
collaborative game theory to tackle these problems and find
applicable and efficient strategies for communities and web
services to maximize their profit.

@@

In this section, we present different web service community models
and focus on the problem of how both web services and community
masters as rational entities would adopt strategies to maximize
their payoff.

@@

In this scenario, we assume the existence of a typical community
managed by its master, and web services need to join it to be able
to get requests from the master. The community master is
characterized by a request rate $(R_{C})$ from users. Each web
service comes with a given QoS ($QoS_{ws}$). The worth of a
community $v(C)$ is set to $Out(C)$ based on Equation \ref{out_c}.

As mentioned in the previous section, the worth of a community is
a function of the throughput and provided QoS of its web service
members. If the throughput rate is more than the master's input
request rate, it means the web services inside the community are
capable of serving more requests than the demand. Considering this
factor, the valuation function is designed to balance the output
performance so that it matches the exact throughput rate and QoS
the web service can provide within the particular community.
%** In the case where the limited tasks are distributed among web services uniformly, the value of coalition would be the proportion of the average QoS times their throughput to rate of available requests. **

In this first scenario, we only consider one grand coalition and
analyze the system from the point of view of one single master web
service and a collection of web services. The master web service
decides which members can join
%or should leave%
the community and distributes the requests and income among its
community members (see Figure \ref{fig_sim1}). The generalization
of this case will be discussed in the next section (Scenario 2).

@@

Our algorithm works as follows. Given an  established community
with a master and some member web services, a web service would
send a \emph{join request} to join  the community. Ideally, the
\emph{core} or \emph{$\epsilon$-core} stability of the group
having this new member should be analyzed. As the normal core
membership algorithm is computationally intractable, we exploit
Proposition \ref{proposition1} and Equation \ref{eq:convex_snow}
to check the convexity of our game having characteristic function
where the new member is added. In this equation (i.e., Equation
\ref{eq:convex_snow}), let $C$ be our community members before the
new web service joins the community. Let  ${i}$ be the new web
service, and then verify the equation for $S$, setting $ S = T /
W1 $ where $W1$ is the set of all possible subsets of the set $N$
having the size $1$. We can relax the equation a bit by adding a
constant $\epsilon$ to the left side of the equation. We call this
method \emph{Depth-1 Convex-Checker} algorithm. If the equation is
satisfied for all $W1$, we let the new web service joins our
community, since the web service will contribute positively enough
to make our new community stable. Since only subsets of size $1$
are checked, the following Proposition holds.

@@

In this scenario, we consider multiple communities managed by
multiple master web services, each of which is providing
independent request pools (see Figure \ref{fig_sim2}). Identical
to the first scenario, master web services form coalitions with
web services. We use coalition structure formation methods to
partition web services into non-empty disjoint coalition
structures. As mentioned in Section \ref{sec:coalition}, the key
fundamental problems we aim to solve is what communities to form
out of the existing web services, and how to divide the payoffs
among the collaborators.

@@

In coalition-formation games, formation of the coalitions is the
most important aspect. The solutions focus on maximizing the
social welfare \cite{
DBLP:conf/ijcai/GrecoMPS11,Sandholm1999209,DBLP:conf/ijcai/RahwanMJ11}.
For any coalition structure $\pi$, let $v_{cs}(\pi)$ denote the
total worth $\sum_{C \in \pi}{v(C)}$, which represents the
\emph{social welfare}. The solution concepts deal with finding the
maximum value for the social welfare over all the coalition
structure $\pi$. There are $centralized$ algorithms for this end,
but these approaches are generally NP-complete. The reason is that
the number of all possible partitions of the set $C$ grows
exponentially with the number of players, and the centralized
algorithms need to iterate through all these partitions.
%These algorithms \cite{DBLP:conf/ijcai/GrecoMPS11, DBLP:conf/ijcai/RahwanMJ11, RePEc:wpa:wuwpga:0110001} are centralized algorithms, where all the complexity. However these algorithms are more intractable than Core stable solutions and practical with some constraints in practice\cite{RePEc:wpa:wuwpga:0110001}.
In our model, we propose using a distributed algorithm where each
community master and web service can be a decision maker and
decide for its own benefit. The aim is to find less complex and
distributed algorithms for forming web services coalitions
\cite{DBLP:journals/igtr/AptW09,Dieckmann02dynamiccoalition,ray2007game}.
The distributed merge-and-split algorithm in
\cite{DBLP:journals/igtr/AptW09} suits our application very well.
It keeps splitting and merging coalitions to partitions which are
preferred by all the players inside those coalitions.

@@

The valuation function $v(C)$ for this scenario is the same as for
Scenario 1 (i.e., \emph{``Web Services and One Community''}).
However, in order to prevent master web services joining the same
community, we set $v(C) = 0$ when $C$ has either none, or more
than one master web service as member.

@@

The solution we propose for communities to ensure  stability is
applying a tax $\epsilon$, which is an amount of cost for those
web services that decide to change communities, which would make
deviation a costly act. However, this would require all the
community coordinators to agree on a same amount of taxation,
being governed by some external entities; otherwise, web services
would join communities charging the lowest amount of tax. Another
viable solution we introduce to our scenario is to stabilize the
game using external subsidies. The reason a game is not stable is
that the community is not making enough revenue to allocate enough
gain to the players. A community master can subside its community
with a constant coefficient value of $\lambda$.
%
%Rewarding a community with high number of quality participants
%with $\lambda v(C)$, where $\lambda \leq 1$.
%
Obviously, with a big value for $\lambda$, it is always possible
to stabilize the community. However, this can be a costly act for
the community masters, so they are interested in the minimum
subside value of $\lambda$ making the community stable. Subsiding
or taxing in order to reduce the bargaining power of sub
coalitions are called $taxation$ \cite{eps346856} methods. We
evaluate the effectiveness of these two methods experimentally
through extensive simulations in the next section.

@@

In the previous experiment, we considered the scenario where all
web services are stable, will not leave the group, and will
fulfill their promised QoS for a good period of time. However, in
real world scenarios of web services, this is not always the case.
This is the reason why the master would be interested in paying
web services in order to keep the group reliable from the end
user's point of view. In our next scenario, we have introduced the
new instability variable $\tau$ ranging from 0 to 1, 0 meaning web
services having no instability issues and will perform as they
claimed until the end of the experiment, and 1 meaning very
unstable web services, which will stop functioning on the first
iteration of the community distributing tasks. Figure
\ref{fig_dynamic_taxtation} illustrates the results of our
experiment having web services with average instability values of
0 to 0.5 and having relative subside value $\lambda$ of 1, 1.3,
1.6, and 2. The \emph{Cost/Income} charts on the right column show
that having subside value of 1.3 incurs the least cost and
increases the community income significantly. Subsiding values of
1.6 and 2 yield high cost to the community and only slightly
increase the community revenue. Moreover, the role of subsiding is
much more obvious when we have unstable web services. In scenarios
where web services are 100\% stable, the subsiding cost will
hardly be compensated by the community revenue.

@@

As mentioned in section \ref{webservice-communities}, communities
are robust service providers with well established market share
and reputation. By maintaining their reputation and performance,
they attract  end users which choose them as service providers to
perform their tasks. The community master is characterized by a
request rate $(R_C)$ from users. Each web service comes with a
given QoS ($QoS_{ws}$) from which the throughput $Th_{ws}$ is
excluded. Throughput is the average rate of tasks a web service
can perform per time unit. Its exclusion from $QoS_{ws}$ allows us
to build our analysis on the particular value of $Th_{ws}$. Thus,
web services perform tasks with an average output quality of
$QoS_{ws}$ and a throughput rate of $Th_{ws}$.

The community master uses a slightly modified \emph{weighted fair
queuing} method to distribute tasks among its members. The goal is
to allocate incoming tasks to web services with a rate matching
the throughput value of $Th_{ws}$. In \emph{weighted fair queuing}
method \emph{all} the input flow is multiplexed along different
paths, however in our case if the input rate $(R_C)$ of the
community is more than the summation of throughput values of the
web services in the community, some of the input tasks will be
queued and served with delay. Thus, the amount of tasks performed
by community is $\sum_{ws \in C}{(Th_{ws})}$ when
$\sum_{ws}{Th_{ws}} \leq R_{C}$. However, when the input rate
$(R_C)$ of the community is less than the summation of throughput
values of the web services in the community,
%the community has more web services having more total throughput value than community's request rate
$(R_C)$ the \emph{weighted fair queuing} algorithm assigns a
weighted task rate of $R_C \times
\frac{Th_{ws}}{\sum_{ws}{Th_{ws}}}$ for each web service ($ws$)
and the total rate of tasks being performed is $R_C$, the
community's receiving request rate.

While distributing tasks, the community master can verify the
performance, throughput and quality of service of   tasks being
performed by web services. It can recognize if web services are
capable of doing the amount of tasks they advertised. If for any
reason there is a decline in quality metrics or throughput, the
community master will announce the new parameters and community
masters and members can consider those values as benchmark for
future performance calculations but also to penalize them. In this
way, players have incentive to reveal their real capabilities to
profit best from the community and to avoid being penalized. In
addition, the system should be dynamic enough to detect and react
to web services quality metrics variation as over time web service
metrics may  degrade or improve, a change that the community
should adjust to.
% Therefore its easy for the system to encourage players to be in some sense incentive compatible in the way that they would profit best by truthfully revealing their capabilities. Also it is important to be dynamic enough to consider web services which may have their quality metrics degraded or even improved over time for any reason and be able to adjust the community with new parameters.

@@

In Example 3, we consider the case of having different communities
with different market share, ${R_C}$ values. Web services also
have a small share of market independently, providing them with a
small task pull. In these kind of scenarios, the solution
considers individual maximization of payoff and also the total
worth of all communities which represents the \emph{social
welfare}. In this example the most efficient partition of web
services is earned by having two coalitions of
$\left\{C_{master_1}, ws_2\right\}$ and $\left\{C_{master_2},
ws_1, ws_3\right\}$, which yields a total value of $32 + 16 = 48$.
In these types of scenarios, the goal is to reach stability,
adopting a distributed approach where all players have the power
of choice on the decision of whether or not they join a coalition.
The communities usually start the game having some established
members, encountering new web services, the communities may
exchange web services and new web services would join them having
at least one player gaining utility, without hurting any other
participant. In this example if we initially having two coalitions
of $\left\{C_{master_1}, ws_2\right\}$ and $\left\{C_{master_2},
ws_1\right\}$ and a ${ws_3}$ as new web service, ${ws_3}$ joining
${C_{master_1}}$ would hurt at least itself or $ws_2$, however
${ws_3}$ joining ${C_{master_2}}$ would not hurt any participants
and ${ws_3}$ would earn more within the community and the
community will have enough web services performing the incoming
tasks from users.

The first two examples illustrate the fact that a community cannot
simply increase its revenue by adding more web services. The web
services and even community owners are autonomous agents and would
deviate and be displeased about the community if new members cause
a drop in their profit. The job of the community master is to
attract as many quality web services it can and keep them
satisfied; hence the group stability is guaranteed. The third
example highlights another type of problem we would like to
address, which is how to form best possible groups of communities,
and allocate web services among communities in a way which would
maximize payoff for of our agents and members already residing in
the communities. In next section, we provide collaborative game
theory based algorithms for our autonomous agents, to tackle these
problems and find applicable and efficient strategies for
communities and web services to maximize their profit.

@@

In this scenario, we assume the existence of a typical community
managed by its master, and web services need to join it to be able
to get requests from the master. The community master is
characterized by a requests rate $(R_{C})$ from users. Each web
service comes with a given QoS ($QoS_{ws}$). The worth of a
community $v(C)$ is set to Out(C) based on equation \ref{out_c}.

As mentioned in previous section, the worth and output of a
community  is a function of the throughput and provided QoS of its
web service members. If the throughput rate is more than the
master's input request rate, it means the web services inside the
community are capable of serving more requests than the demand.
Considering this factor, the valuation function is designed to
balance the output performance so that it matches the exact
throughput rate and QoS the web service can provide within the
particular community.
%** In the case where the limited tasks are distributed among web services uniformly, the value of coalition would be the proportion of the average QoS times their throughput to rate of available requests. **

In this first scenario, we only consider one grand coalition and
analyze the system from the point of view of one single master web
service and a collection of web services. The master web service
decides which members can join
%or should leave%
the community and distributes the requests and income among its
community members (see Figure \ref{fig_sim1}).

>>>>

\textbf{Contributions.} In this paper, we use game theory to
propose a cooperative game model for the aggregation of web
services within communities. The solution concepts of our
cooperative game seeks to find efficient ways of forming
coalitions (teams) of web services so that they can maximize their
gain and payoff, and distribute the gain in a fair way among all
the web services. Achieving fairness when the gain is distributed
among the community members is the main factor to keep the
coalition stable as no web service will expect to gain better by
deviating from the community. In other words, the coalition is
made efficient if all the members are satisfied. We analyze the
game model using two scenarios. The first one simply considers one
community and many web services interested to join it. The second
scenario, which generalizes the first one, includes the
possibility of joining different already established communities.
We first propose a representation function for communities of web
services based on their QoS attributes. By using this function, we
can evaluate the $worth$ of each community of web services. When
facing new membership requests, a typical community master checks
whether the new coalition having the old and new set of web
services will keep the community stable or not. The community
coordinate will reject the membership requests if it finds out that
the new coalition would be unstable, preventing $any$ subset of
web services from gaining significantly more by deviating from the
community and joining other communities or forming new ones. The
computation of solutions for cooperative game theory problems is
combinatorial in nature and proven to be NP-complete
\cite{Algorithmic}, making this computation impractical in real
world applications. However, using the concepts of coalition
stability, we propose approximation algorithms running in
polynomial time providing web services and community coordinators with
applicable and near-optimal decision making mechanisms.

@@

%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 3 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table*}[!t]
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
\caption{Example 3} \label{example_3} \centering
\begin{tabular}{c c c c}
\hline
$WS$ & $QoS_{ws}$ & $Th_{ws}$ & $\text{\emph{Input Task Rate}}$\\
\hline
1 & 0.8 & 10 & 5\\
2 & 0.8 & 20 & 5\\
3 & 0.8 & 30 & 5\\
\hline\\
\end{tabular}
%\end{table}
%
%\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
% \caption{Three web services}
\label{example_3_2} \centering
\begin{tabular}{l l || l l}
\hline
Community & Worth & Community & Worth\\
\hline
$\left\{C_{1}\right\}$ & 0 & $\left\{C_{2}\right\}$ & 0\\
$\left\{C_{1}, ws_1\right\}$ & 8 & $\left\{C_{2}, ws_1\right\}$ & 8\\
$\left\{C_{1}, ws_2\right\}$ & 16 & $\left\{C_{2}, ws_2\right\}$ & 16\\
$\left\{C_{1}, ws_3\right\}$ & 16 & $\left\{C_{2}, ws_3\right\}$ & 24\\
$\left\{C_{1}, ws_1, ws_2\right\}$ & 16 & $\left\{C_{2}, ws_1, ws_2\right\}$ & 24\\
$\left\{C_{1}, ws_1, ws_3\right\}$ & 16 & $\left\{C_{2}, ws_1, ws_3\right\}$ & 32\\
$\left\{C_{1}, ws_2, ws_3\right\}$ & 16 & $\left\{C_{2}, ws_2, ws_3\right\}$ & 32\\
$\left\{C_{1}, ws_1, ws_2, ws_3\right\}$ & 16 & $\left\{C_{2}, ws_1, ws_2, ws_3\right\}$ & 32\\
$\left\{C_{1}, C_{ms_2}, ...\right\}$ & 0 & $\left\{ws_1\right\}$ & 6.8\\
$\left\{ws_2\right\}$ & 4.2 & $\left\{ws_3\right\}$ & 6.8\\
\hline
Community $R_{C_1}$: 20 \\ Community $R_{C_2}$: 40\\
\hline
\end{tabular}
\end{table*}
%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 3 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In Example 3, we consider the case of having different communities
with different market shares represented by ${R_C}$ values. Web
services also have a small share of market independently,
providing them with a small task pull. In these kind of scenarios,
the solution considers individual maximization of payoff and also
the total worth of all communities which represents the
\emph{social welfare}. In this example, the most efficient
partition of web services is earned by having two coalitions of
$\left\{C_{1}, ws_2\right\}$ and $\left\{C_{2},
ws_1, ws_3\right\}$, which yields a total value of $32 + 16 = 48$.
In these types of scenarios, the goal is to reach stability,
adopting a distributed approach where all players have the power
to decide about joining a coalition or not. The communities
usually start the game having some established members. They may
exchange web services and new web services would join them having
at least one player gaining utility without hurting any other
participant. In this example, if we initially having two
coalitions of $\left\{C_{1}, ws_2\right\}$ and
$\left\{C_{2}, ws_1\right\}$ and a ${ws_3}$ as new web
service, ${ws_3}$ joining ${C_{1}}$ would hurt at least
itself or $ws_2$; however, ${ws_3}$ joining ${C_{2}}$ would
not hurt any participant and ${ws_3}$ would earn more within the
community and the community will have enough web services
performing the incoming tasks from users.

The first two examples illustrate the fact that a community cannot
simply increase its revenue by adding more web services. The web
services and even community owners are autonomous agents and would
deviate and be displeased about the community if new members cause
a drop in their profit. The job of the community coordinator is to
attract as many quality web services it can and keep them
satisfied; hence the group stability is guaranteed. The third
example highlights another type of problem we would like to
address, which is how to form best possible groups of communities,
and allocate web services among communities in a way which would
maximize the payoff of members already residing in the
communities. In the next section, we provide algorithms based on
collaborative game theory to tackle these problems and find
applicable and efficient strategies for communities and web
services to maximize their profit.

@@

In this section, we present different web service community models
and focus on the problem of how both web services and community
coordinators as rational entities would adopt strategies to maximize
their payoff.

@@

In this scenario, we assume the existence of a typical community
managed by its coordinator, and web services need to join it to be able
to get requests from the community. The community coordinator is
characterized by a request rate $(R_{C})$ from users. Each web
service comes with a given QoS ($QoS_{ws}$). The worth of a
community $v(C)$ is set to $Out(C)$ based on Equation \ref{out_c}.

As mentioned in the previous section, the worth of a community is
a function of the throughput and provided QoS of its web service
members. If the throughput rate is more than the community's input
request rate, it means the web services inside the community are
capable of serving more requests than the demand. Considering this
factor, the valuation function is designed to balance the output
performance so that it matches the exact throughput rate and QoS
the web service can provide within the particular community.
%** In the case where the limited tasks are distributed among web services uniformly, the value of coalition would be the proportion of the average QoS times their throughput to rate of available requests. **

In this first scenario, we only consider one grand coalition and
analyze the system from the point of view of one community and a collection of web services. The community coordinator
decides which members can join
%or should leave%
the community and distributes the requests and income among its
community members (see Figure \ref{fig_sim1}). The generalization
of this case will be discussed in the next section (Scenario 2).

@@

Our algorithm works as follows. Given an established community
with a coordinator and some member web services, a web service would
send a \emph{join request} to join  the community. Ideally, the
\emph{core} or \emph{$\epsilon$-core} stability of the group
having this new member should be analyzed. As the normal core
membership algorithm is computationally intractable, we exploit
Proposition \ref{proposition1} and Equation \ref{eq:convex_snow}
to check the convexity of our game having characteristic function
where the new member is added. In this equation (i.e., Equation
\ref{eq:convex_snow}), let $C$ be our community members before the
new web service joins the community. Let  ${i}$ be the new web
service, and then verify the equation for $S$, setting $ S = T /
W1 $ where $W1$ is the set of all possible subsets of the set $N$
having the size $1$. We can relax the equation a bit by adding a
constant $\epsilon$ to the left side of the equation. We call this
method \emph{Depth-1 Convex-Checker} algorithm. If the equation is
satisfied for all $W1$, we let the new web service joins our
community, since the web service will contribute positively enough
to make our new community stable. Since only subsets of size $1$
are checked, the following Proposition holds.

@@

In this scenario, we consider multiple communities managed by
multiple coordinators, each of communities having
independent request pools (see Figure \ref{fig_sim2}). 
%Identical to the first scenario, master web services form coalitions with web services. 
We use coalition structure formation methods to
partition web services into non-empty disjoint coalition
structures. As mentioned in Section \ref{sec:coalition}, the key
fundamental problems we aim to solve is what communities to form
out of the existing web services, and how to divide the payoffs
among the collaborators.

@@

In coalition-formation games, formation of the coalitions is the
most important aspect. The solutions focus on maximizing the
social welfare \cite{
DBLP:conf/ijcai/GrecoMPS11,Sandholm1999209,DBLP:conf/ijcai/RahwanMJ11}.
For any coalition structure $\pi$, let $v_{cs}(\pi)$ denote the
total worth $\sum_{C \in \pi}{v(C)}$, which represents the
\emph{social welfare}. The solution concepts deal with finding the
maximum value for the social welfare over all the coalition
structure $\pi$. There are $centralized$ algorithms for this end,
but these approaches are generally NP-complete. The reason is that
the number of all possible partitions of the set $C$ grows
exponentially with the number of players, and the centralized
algorithms need to iterate through all these partitions.
%These algorithms \cite{DBLP:conf/ijcai/GrecoMPS11, DBLP:conf/ijcai/RahwanMJ11, RePEc:wpa:wuwpga:0110001} are centralized algorithms, where all the complexity. However these algorithms are more intractable than Core stable solutions and practical with some constraints in practice\cite{RePEc:wpa:wuwpga:0110001}.
In our model, we propose using a distributed algorithm where each
community coordinator and web service can be a decision maker and
decide for its own benefit. The aim is to find less complex and
distributed algorithms for forming web services coalitions
\cite{DBLP:journals/igtr/AptW09,Dieckmann02dynamiccoalition,ray2007game}.
The distributed merge-and-split algorithm in
\cite{DBLP:journals/igtr/AptW09} suits our application very well.
It keeps splitting and merging coalitions to partitions which are
preferred by all the players inside those coalitions.

@@

The valuation function $v(C)$ for this scenario is the same as for
Scenario 1 (i.e., \emph{``Web Services and One Community''}).
%However, in order to prevent master web services joining the same community, we set $v(C) = 0$ when $C$ has either none, or more than one master web service as member.

@@

The solution we propose for communities to ensure  stability is
applying a tax $\epsilon$, which is an amount of cost for those
web services that decide to change communities, which would make
deviation a costly act. However, this would require all the
community coordinators to agree on a same amount of taxation,
being governed by some external entities; otherwise, web services
would join communities charging the lowest amount of tax. Another
viable solution we introduce to our scenario is to stabilize the
game using external subsidies. The reason a game is not stable is
that the community is not making enough revenue to allocate enough
gain to the players. A community coordinator can subside its community
with a constant coefficient value of $\lambda$.
%
%Rewarding a community with high number of quality participants
%with $\lambda v(C)$, where $\lambda \leq 1$.
%
Obviously, with a big value for $\lambda$, it is always possible
to stabilize the community. However, this can be a costly act for
the community coordinators, so they are interested in the minimum
subside value of $\lambda$ making the community stable. Subsiding
or taxing in order to reduce the bargaining power of sub
coalitions are called $taxation$ \cite{eps346856} methods. We
evaluate the effectiveness of these two methods experimentally
through extensive simulations in the next section.

@@

In the previous experiment, we considered the scenario where all
web services are stable, will not leave the group, and will
fulfill their promised QoS for a good period of time. However, in
real world scenarios of web services, this is not always the case.
This is the reason why the community coordinator would be interested in paying
web services in order to keep the group reliable from the end
user's point of view. In our next scenario, we have introduced the
new instability variable $\tau$ ranging from 0 to 1, 0 meaning web
services having no instability issues and will perform as they
claimed until the end of the experiment, and 1 meaning very
unstable web services, which will stop functioning on the first
iteration of the community distributing tasks. Figure
\ref{fig_dynamic_taxtation} illustrates the results of our
experiment having web services with average instability values of
0 to 0.5 and having relative subside value $\lambda$ of 1, 1.3,
1.6, and 2. The \emph{Cost/Income} charts on the right column show
that having subside value of 1.3 incurs the least cost and
increases the community income significantly. Subsiding values of
1.6 and 2 yield high cost to the community and only slightly
increase the community revenue. Moreover, the role of subsiding is
much more obvious when we have unstable web services. In scenarios
where web services are 100\% stable, the subsiding cost will
hardly be compensated by the community revenue.

@@

As mentioned in section \ref{webservice-communities}, communities
are robust service providers with well established market share
and reputation. By maintaining their reputation and performance,
they attract  end users which choose them as service providers to
perform their tasks. The community coordinator is characterized by a
request rate $(R_C)$ from users. Each web service comes with a
given QoS ($QoS_{ws}$) from which the throughput $Th_{ws}$ is
excluded. Throughput is the average rate of tasks a web service
can perform per time unit. Its exclusion from $QoS_{ws}$ allows us
to build our analysis on the particular value of $Th_{ws}$. Thus,
web services perform tasks with an average output quality of
$QoS_{ws}$ and a throughput rate of $Th_{ws}$.

The community coordinator uses a slightly modified \emph{weighted fair
queuing} method to distribute tasks among its members. The goal is
to allocate incoming tasks to web services with a rate matching
the throughput value of $Th_{ws}$. In \emph{weighted fair queuing}
method \emph{all} the input flow is multiplexed along different
paths, however in our case if the input rate $(R_C)$ of the
community is more than the summation of throughput values of the
web services in the community, some of the input tasks will be
queued and served with delay. Thus, the amount of tasks performed
by community is $\sum_{ws \in C}{(Th_{ws})}$ when
$\sum_{ws}{Th_{ws}} \leq R_{C}$. However, when the input rate
$(R_C)$ of the community is less than the summation of throughput
values of the web services in the community,
%the community has more web services having more total throughput value than community's request rate
$(R_C)$ the \emph{weighted fair queuing} algorithm assigns a
weighted task rate of $R_C \times
\frac{Th_{ws}}{\sum_{ws}{Th_{ws}}}$ for each web service ($ws$)
and the total rate of tasks being performed is $R_C$, the
community's receiving request rate.

While distributing tasks, the community coordinator can verify the
performance, throughput and quality of service of   tasks being
performed by web services. It can recognize if web services are
capable of doing the amount of tasks they advertised. If for any
reason there is a decline in quality metrics or throughput, the
community coordinator will announce the new parameters and community
coordinators and members can consider those values as benchmark for
future performance calculations but also to penalize them. In this
way, players have incentive to reveal their real capabilities to
profit best from the community and to avoid being penalized. In
addition, the system should be dynamic enough to detect and react
to web services quality metrics variation as over time web service
metrics may  degrade or improve, a change that the community
should adjust to.
% Therefore its easy for the system to encourage players to be in some sense incentive compatible in the way that they would profit best by truthfully revealing their capabilities. Also it is important to be dynamic enough to consider web services which may have their quality metrics degraded or even improved over time for any reason and be able to adjust the community with new parameters.

@@

In Example 3, we consider the case of having different communities
with different market share, ${R_C}$ values. Web services also
have a small share of market independently, providing them with a
small task pull. In these kind of scenarios, the solution
considers individual maximization of payoff and also the total
worth of all communities which represents the \emph{social
welfare}. In this example the most efficient partition of web
services is earned by having two coalitions of
$\left\{C_{1}, ws_2\right\}$ and $\left\{C_{2},
ws_1, ws_3\right\}$, which yields a total value of $32 + 16 = 48$.
In these types of scenarios, the goal is to reach stability,
adopting a distributed approach where all players have the power
of choice on the decision of whether or not they join a coalition.
The communities usually start the game having some established
members, encountering new web services, the communities may
exchange web services and new web services would join them having
at least one player gaining utility, without hurting any other
participant. In this example if we initially having two coalitions
of $\left\{C_{1}, ws_2\right\}$ and $\left\{C_{2},
ws_1\right\}$ and a ${ws_3}$ as new web service, ${ws_3}$ joining
${C_{1}}$ would hurt at least itself or $ws_2$, however
${ws_3}$ joining ${C_{2}}$ would not hurt any participants
and ${ws_3}$ would earn more within the community and the
community will have enough web services performing the incoming
tasks from users.

The first two examples illustrate the fact that a community cannot
simply increase its revenue by adding more web services. The web
services and even community owners are autonomous agents and would
deviate and be displeased about the community if new members cause
a drop in their profit. The job of the community coordinator is to
attract as many quality web services it can and keep them
satisfied; hence the group stability is guaranteed. The third
example highlights another type of problem we would like to
address, which is how to form best possible groups of communities,
and allocate web services among communities in a way which would
maximize payoff for of our agents and members already residing in
the communities. In next section, we provide collaborative game
theory based algorithms for our autonomous agents, to tackle these
problems and find applicable and efficient strategies for
communities and web services to maximize their profit.

@@

In this scenario, we assume the existence of a typical community
managed by its coordinator, and web services need to join it to be able
to get requests from the community. The community coordinator is
characterized by a requests rate $(R_{C})$ from users. Each web
service comes with a given QoS ($QoS_{ws}$). The worth of a
community $v(C)$ is set to Out(C) based on equation \ref{out_c}.

As mentioned in previous section, the worth and output of a
community  is a function of the throughput and provided QoS of its
web service members. If the throughput rate is more than the
community's input request rate, it means the web services inside the
community are capable of serving more requests than the demand.
Considering this factor, the valuation function is designed to
balance the output performance so that it matches the exact
throughput rate and QoS the web service can provide within the
particular community.
%** In the case where the limited tasks are distributed among web services uniformly, the value of coalition would be the proportion of the average QoS times their throughput to rate of available requests. **

In this first scenario, we only consider one grand coalition and
analyze the system from the point of view of one single community coordinator 
and a collection of web services. The community coordinator 
decides which members can join
%or should leave%
the community and distributes the requests and income among its
community members (see Figure \ref{fig_sim1}).
